### 2019-08-08 thesis.tex
new text

\section{Solar and space physics}
\label{sec:solar-physics}
The solar system is permeated with a constant plasma flow of solar origin.
This tenuous and rapid flowing plasma is the solar wind. It enfolds the Earth
as it travels outward the solar system, creating a region around the Sun that
extends to approximately $140\unit{AU}$ in the surrounding galactic space.
This region, called heliosphere, is the domain of solar and space physics. In
the boundaries of the heliosphere, the outward pressure of the solar plasma
balances the inward pressure from the interstellar medium. This interface
region, the heliopause, limits the volume in the galactic environment that is
under the influence of the solar wind \cite{NAP13060}. A general depiction of
the heliosphere and its main boundaries is depicted in \autoref{figD1}, where
the termination shock separates the inner and outer regions of the heliosphere.

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.48\textwidth]{Heliosphere_main_Boundaries}
    \caption{Main boundaries of the heliosphere.
      {\footnotesize Credit:}
      \href{https://science.nasa.gov/heliophysics/focus-areas/heliosphere}
      {\footnotesize NASA}{\footnotesize , accessed at 07/08/2019}.}
    \label{figD1}
  \end{center}
\end{figure}

>>>>

\section{Solar and space physics}
\label{sec:solar-physics}
The domain of solar and space physics is the \emph{heliosphere}, a cavity in
the interstellar medium, created by the constant supersonic flow of solar
plasma that permeates the interplanetary space. This region encloses the solar
system and extends for approximately $140\unit{AU}$ in the surrounding galactic
space. Its outer limit is the \emph{heliopause}, an interface zone where the
outgoing pressure of the solar plasma balances the incoming pressure from the
interstellar medium. This comet-shaped plasma bubble, has an inner boundary, the
\emph{termination shock}, which delimits the sphere of absolute influence of the
solar plasma. Outside the termination shock, the solar wind particles start to
be subjected to increasing external pressure, transitioning to a subsonic flow
that blends with the interstellar medium at roughly $100\unit{AU}$ from the Sun.
Beyond the termination shock, lies the heliosheath, a so-far-unexplored zone
that extends out to the heliopause, separating the solar domain from the nearby
galactic region \cite{NAP13060}. In \autoref{figD1}, we have a depiction of the
regions and boundaries described above, and the current location of both Voyager
missions, that are already outside the heliosphere, in the interstellar space.
\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{solar_system_env.png}
    \caption{Main boundaries of the heliosphere and the location of both
      Voyager missions.}
      {\footnotesize Credit:}
      \href{https://voyager.jpl.nasa.gov/news/details.php?article_id=112}
      {\footnotesize NASA/JPL-Caltech}{\footnotesize , accessed at 08/08/2019.}
    \label{figD1}
  \end{center}
\end{figure}
